### 2025-09-03 download-football-data.qmd
20250902 - data dictionaries

@@

@HoFFPlayerIDs provide a Data Dictionary for fantasy player ID data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_ff_playerids.html>

@@

@@

@HoSchedules provide a Data Dictionary for game schedules data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_schedules.html>

@@

@HoCombine provide a Data Dictionary for data from the NFL Combine at the following link: <https://nflreadr.nflverse.com/articles/dictionary_combine.html>

@@

@HoDraftPicks provide a Data Dictionary for draft picks data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_draft_picks.html>

@@

@HoDepthCharts provide a Data Dictionary for data from weekly depth charts at the following link: <https://nflreadr.nflverse.com/articles/dictionary_depth_charts.html>

@@

@SharpeTrades provides a Data Dictionary for NFL trade data at the following link: <https://github.com/nflverse/nfldata/blob/master/DATASETS.md#trades>

@@

To download play-by-play data from prior weeks and seasons, we can use the `nflreadr::load_pbp()` function of the `nflreadr` package [@R-nflreadr].
We add a progress bar using the `progressr::with_progress()` function from the `progressr` package [@R-progressr] because it takes a while to run.
@HoPBP provide a Data Dictionary for the play-by-play data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_pbp.html>

@@

@HoParticipation provide a Data Dictionary for the participation data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_participation.html>

@@

We can download historical week-by-week actual player statistics using the `nflreadr::load_player_stats()` function from the `nflreadr` package [@R-nflreadr].
@HoPlayerStats provide a Data Dictionary for statistics for offensive players at the following link: <https://nflreadr.nflverse.com/articles/dictionary_player_stats.html>.
@HoPlayerStatsDefense provide a Data Dictionary for statistics for defensive players at the following link: <https://nflreadr.nflverse.com/articles/dictionary_player_stats_def.html>.

@@

@HoInjuries provide a Data Dictionary for injury data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_injuries.html>

@@

@HoSnapCounts provide a Data Dictionary for snap counts data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_snap_counts.html>

@@

@HoQBR provide a Data Dictionary for ESPN QBR data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_espn_qbr.html>

@@

@HoNextGenStats provide a Data Dictionary for NFL Next Gen Stats data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_nextgen_stats.html>

@@

@@

@@

@HoContracts provide a Data Dictionary for player contracts data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_contracts.html>

@@

@HoFTNCharting provide a Data Dictionary for FTN Charting data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_ftn_charting.html>

@@

@HoFantasyProsRankings provide a Data Dictionary for FantasyPros ranking data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_ff_rankings.html>

@@

@HoOpportunity provide a Data Dictionary for expected fantasy points data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_ff_opportunity.html>

>>>>

You can access a data dictionary via `R` using the following syntax:

nflreadr::dictionary_players
```

You can download the data using the following syntax:

@@

@HoFFPlayerIDs provide a Data Dictionary for fantasy player ID data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_ff_playerids.html>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_ff_playerids
```

You can download the data using the following syntax:

@@

You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_roster_status
nflreadr::dictionary_rosters
```

You can download the data using the following syntax:

@@

@HoSchedules provide a Data Dictionary for game schedules data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_schedules.html>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_schedules
```

You can download the data using the following syntax:

@@

@HoCombine provide a Data Dictionary for data from the NFL Combine at the following link: <https://nflreadr.nflverse.com/articles/dictionary_combine.html>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_combine
```

You can download the data using the following syntax:

@@

@HoDraftPicks provide a Data Dictionary for draft picks data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_draft_picks.html>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_draft_picks
```

You can download the data using the following syntax:

@@

@HoDepthCharts provide a Data Dictionary for data from weekly depth charts at the following link: <https://nflreadr.nflverse.com/articles/dictionary_depth_charts.html>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_depth_charts
```

You can download the data using the following syntax:

@@

@SharpeTrades provides a Data Dictionary for NFL trade data at the following link: <https://github.com/nflverse/nfldata/blob/master/DATASETS.md#trades>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_trades
```

You can download the data using the following syntax:

@@

To download play-by-play data from prior weeks and seasons, we can use the `nflreadr::load_pbp()` function of the `nflreadr` package [@R-nflreadr].
We add a progress bar using the `progressr::with_progress()` function from the `progressr` package [@R-progressr] because it takes a while to run.
@HoPBP provide a Data Dictionary for the play-by-play data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_pbp.html>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_pbp
```

You can download the data using the following syntax:

@@

@HoParticipation provide a Data Dictionary for the participation data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_participation.html>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_participation
```

You can download the data using the following syntax:

@@

We can download historical week-by-week actual player statistics using the `nflreadr::load_player_stats()` function from the `nflreadr` package [@R-nflreadr].
@HoPlayerStats provide a Data Dictionary for statistics for offensive players at the following link: <https://nflreadr.nflverse.com/articles/dictionary_player_stats.html>.
@HoPlayerStatsDefense provide a Data Dictionary for statistics for defensive players at the following link: <https://nflreadr.nflverse.com/articles/dictionary_player_stats_def.html>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_player_stats
```

You can download the data using the following syntax:

@@

@HoInjuries provide a Data Dictionary for injury data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_injuries.html>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_injuries
```

You can download the data using the following syntax:

@@

@HoSnapCounts provide a Data Dictionary for snap counts data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_snap_counts.html>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_snap_counts
```

You can download the data using the following syntax:

@@

@HoQBR provide a Data Dictionary for ESPN QBR data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_espn_qbr.html>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_espn_qbr
```

You can download the data using the following syntax:

@@

@HoNextGenStats provide a Data Dictionary for NFL Next Gen Stats data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_nextgen_stats.html>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_nextgen_stats
```

You can download the data using the following syntax:

@@

You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_pfr_passing
```

@@

You can download the data using the following syntax:

@@

@HoContracts provide a Data Dictionary for player contracts data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_contracts.html>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_contracts
```

You can download the data using the following syntax:

@@

@HoFTNCharting provide a Data Dictionary for FTN Charting data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_ftn_charting.html>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_ftn_charting
```

You can download the data using the following syntax:

@@

@HoFantasyProsRankings provide a Data Dictionary for FantasyPros ranking data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_ff_rankings.html>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_ff_rankings
```

You can download the data using the following syntax:

@@

@HoOpportunity provide a Data Dictionary for expected fantasy points data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_ff_opportunity.html>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_ff_opportunity
```

You can download the data using the following syntax:
